---
title: "Demonstration of multiRDD package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demonstration of multiRDD package}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(ggplot2)
library(tidyverse)
library( arm )
library(multiRDD)

```

First load the library:

```{r setup}
library(multiRDD)
```


To illustrate we need a demonstration dataset.
The `multiRDD` package includes some code to generate such data, whcih is useful for simulations, etc., as well.
Generate data via the `gen.data()` method, as so:

```{r}

#par.sim<-c(0.7,0.3,0.05,0,0.07,0.07,0.025,0 ,0.4,1,1,0.2)
par.sim<-data.frame(ao.m=.7,ao.sd=.3,bo.m=.05,bo.sd=.025,a1.m=.07,
                  a1.sd=.07,b1.m=.025,b1.sd=.025,obs.se=.4,Rmean=1,hopt=1,ICCR=.2)
par.sim

#Data is generated using the following data generating functions 
#Control
#  Y0<-a0+b0*running
#Treatment
#Y1<-Y0+a1+b1*running
#a0 is the intercept for the control
#a1 is the change in the intercept for the treatment, (the treatment effect)
#b0 is the relationship between outcome and the running variable for the control
#b1 is the relationship between outcome and the running variable interacted with treatment
  
names<-c("a0","b0","a1","b1")
means<-as.numeric(dplyr::select(par.sim,dplyr::contains(".m")))
sds<-as.numeric(dplyr::select(par.sim,dplyr::contains(".sd")))
parameters.reg<-data.frame(names,means,sds)
  
#these are the other parameters to generate the schools
#ICCR : ICC of the running variable across schools
#obs.se:Is the observation level standard error
#Rmean: is the grand mean of the running variable is sd's away from the cut point 
#hopt: is the bandwidth

parameters.gen<-par.sim %>% 
                dplyr::select(-dplyr::contains(".sd")) %>%  
                dplyr::select(-dplyr::contains(".m"))
parameters.gen

sim.sample = gen.data( TC = 150, nmean = 130, 
                       parameters.reg = parameters.reg,
                       obs.se = parameters.gen$obs.se, Rmean = parameters.gen$Rmean )
sim.sample <- sim.sample %>% dplyr::select(cl.id,running,Y)
```

The data we need are cluster IDs, the value of the running variable, and the outcome.
The running variable is assumed to have been centered by cluster so 0 is the threshold value.

```{r}
head( sim.sample )
```



# Pre-process data (bandwidth subsetting)

Before analysis, the data needs to be subset to be in bandwidth.
We also recommend dropping small clusters as well, as they can be quite unstable (especially with respect to estimating standard errors for the meta analysis approach).

```{r}
df.test<-sim.sample %>% 
    filter(running<1, running>-1) %>% 
    mutate(cl.id=as.factor(cl.id)) %>%
    group_by(cl.id) %>%
    dplyr::mutate(inbwT=sum(running<0),inbwNT=sum(running>=0)) %>% 
    filter(inbwNT>10 & inbwT>10) %>%
    ungroup()
df.test

```

# Analyze the data

We have four methods for analysis.

The LLR approach:

```{r}

reg.LLR(df.test,clusterid="cl.id",runvar = "running", outcomevar = "Y",less.than = TRUE)

```


The meta-analysis approach:
```{r}

reg.Meta(df.test,clusterid="cl.id",runvar = "running", outcomevar = "Y",less.than = TRUE)

```

The Restricted FIRC approach
```{r}

model = c("pool","pool","pp","up")
names(model)=c("running","tr.rn","treat","intercept")

reg.FIRC(df.test,clusterid="cl.id",runvar = "running", outcomevar = "Y",less.than = TRUE,model=model)

```

And the Unrestricted FIRC approach (the `reg.FIRC` method, depending on passed parameters, allows for different modeling approaches):

```{r}
model = c("pp","pp","pp","up")
names(model)=c("running","tr.rn","treat","intercept")

reg.FIRC(df.test,clusterid="cl.id",runvar = "running", outcomevar = "Y",less.than = TRUE,model=model)
```
